\textcolor{red}{Simple} connectome inference using partial correlation from imaging calcium signal

### 2014-06-17 article.tex
wording

% Solution

In this paper, we describe a simple and a theoretically grounded approach
based on partial correlation\footnote{Source code is available at
\url{https://github.com/asutera/kaggle-connectomics}.} to infer the neural
network, which is the winning method of the Connectomics challenge
\footnote{\url{http://connectomics.chalearn.org}}.

The rest of the paper is structured as follows: Section \ref{sec:filter}
describes the pre-processing applied on fluorescent calcium timeseries;
Section \ref{sec:inference} presents the proposed approach and
their theoretical properties; Section \ref{sec:results} provide
empirical analysis and comparison with other network inference method,
whereas Section \ref{sec:conclusion} discusses our work and provides further
research directions.

>>>>

% Solution
In this paper, we describe the winning method of the Connectomics challenge
\footnote{\url{http://connectomics.chalearn.org}}, a simple and theoretically
grounded approach, based on partial correlation\footnote{Source code is available
at \url{https://github.com/asutera/kaggle-connectomics}.} to infer the neural
network. The rest of the paper is structured as follows: Section \ref{sec:filter}
describes the pre-processing applied on fluorescent calcium timeseries;
Section \ref{sec:inference} presents the proposed approach and
their theoretical properties; Section \ref{sec:results} provide
empirical analysis and comparison with other network inference method,
whereas Section \ref{sec:conclusion} discusses our work and provides further
research directions.
